### 2023-10-19 paper/draft.tex

What is the formula for $\alpha_i$?  $\mathcal{O}(n)$ algorithm for computing all $\alpha_i$ given an index $\{\pi_i\}_{1\leq i\leq n}$ that sorts $\{f(x_i)_{k+1}\}_{1\leq i \leq n}$?

J: Informally, $\alpha_i$ should be a value between 1 and n-1, denoting the number of instances that have higher estimated confidence than  $f(x_i)_{k+1}$.

@@

>>>>

What is the formula for $\alpha_i$? \\
$\mathcal{O}(n)$ algorithm for computing all $\alpha_i$ given an index $\{\pi_i\}_{1\leq i\leq n}$ that sorts $\{f(x_i)_{k+1}\}_{1\leq i \leq n}$?

\begin{align} % number of samples in between each unique integration point
    \mathcal{C}_j = %
    \frac{1}{n-1} 
    \sum_{\substack{h=1 \\ j \neq h}}^n \mathbb{I}[f(x_h)_{k+1} > f(x_j)_{k+1}] \\ %higher CSF than point j
    \alpha_i =  \mathcal{C}_{\pi_i} - \mathcal{C}_{\pi_{i+1}}     
\end{align}

\begin{align}
    \frac{1}{n} \sum_{i=1}^{n-1} \frac{\sum_{j=i+1}^n\ell([f(x_{i:n})]_{1:k},y_j)}{(n-i)}
\end{align}

\begin{exmp}[simple]\hspace{0.1cm}

    $f(X)_{k+1}$ = [5, 2, 4]

    $\ell([f(X)]_{1:k}, Y)$ = [0, 1, 0]

    $\pi$ = [1,2,0]

\end{exmp}

\section*{Updates 18/10}

J: as it is implemented in \cite{jaeger2023a}, the alphas/weights denote the number of instances between each contiguous pair of thresholds (in our case based on $f(X)_{k+1}$). 
If we consider each individual confidence estimate as an integration point, the stepsize between them (i.e. alpha) will be a constant $1/N$.

%WRONG: J: Informally, $\alpha_i$ should be a value between 1 and n-1, denoting the number of instances that have higher estimated confidence than  $f(x_i)_{k+1}$. 
%The most efficient way to obtain is by sorting $f(X)_{k+1}$ in ascending order ( O(nlogn) average case with comparison-based sort such as timsort [default in Python]), then iterate. 
%https://stackoverflow.com/questions/13603042/what-is-the-fastest-way-to-get-a-sorted-unique-list-in-python

@@

\section*{Updates }

\subsection{Literature review on differentiable \AURC}

\cite{cao2022generalizing} close in spirit, dependent on cost, similarly defines it as a $K+1$ classification problem.
